\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
working-updated

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=2000   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000     
}
}     
\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations. Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
\label{fig:3b_heteheleshaw_10}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000    
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.75cm} (b) flow at t=24000     
}
}     
\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers. At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
\label{fig:3c_heteheleshaw_10}
\end{figure}
\clearpage
